Optimal (Multiway) Spatial Joins

### 2024-05-28 msj.tex
yufei

\begin{figure*}
    \begin{tabular}{cccc}
        \hspace{-5mm}
        \includegraphics[height=45mm]{./artwork/alg-ex2-a} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex2-b} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex2-c} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex2-d} \\
        \hspace{-5mm} (a) $R_1$, $R_2$, $H$, and $V$ &
        \hspace{-4mm} (b) $R_1$, $H'$, and $V$ &
        \hspace{-4mm} (c) $R_1$, $R_2$, $H'$, and $V$ &
        \hspace{-4mm} (d) $R_2$ and $H^*$
    \end{tabular}
    \figcapup
    \caption{Finding H-V $k$-SJ result tuples of type 2 ($k = 4$)}
    \label{fig:hv:type2:ex}
    \figcapdown
\end{figure*}

@@

\noindent {\underline{\em Example 5.2.}} In Figure~\ref{fig:guard}a, segment $h_1$ has no left-covering rectangle in $R_2$ and thus has no trimmed segment. Segment $h_2$ has one left-covering rectangle in $R_2$, which is $\beta_1$. As the entire $h_2$ is covered by $\beta_1$, it is equivalent to its trimmed segment $h_2'$; see Figure~\ref{fig:hv:type2:ex}b. Segment $h_3$ has two left-covering rectangles in $R_2$, which are $\beta_2$ and $\beta_3$. The right endpoint of its trimmed segment $h_3'$, as shown in Figure~\ref{fig:guard}b, is decided by the right edge of $\beta_3$. Therefore, $H' = \set{h_2', h_3'}$. It is clear from Figure~\ref{fig:guard}b that $\J(R_1, , H', V)$ has 3 tuples: $\bm{t}_1 = (\alpha, h_2', v_1), \bm{t}_2 = (\alpha, h_3', v_1)$, and $\bm{t}_3 = (\alpha, h_3', v_2)$.
\qed

@@

\noindent {\underline{\em Example 5.3.}} For $\bm{t}_1 = (\alpha, h_2', v_1) \in \J(R_1, , H', V)$.
Therefore, $H' = \set{h_2', h_3'}$. It is clear from Figure~\ref{fig:guard}b that $\J(R_1, , H', V)$ has 3 tuples: $\bm{t}_1 = (\alpha, h_2', v_1), \bm{t}_2 = (\alpha, h_3', v_1)$, and $\bm{t}_3 = (\alpha, h_3', v_2)$.

>>>>

\begin{figure*}
    \begin{tabular}{cccc}
        \hspace{-5mm}
        \includegraphics[height=45mm]{./artwork/alg-ex2-a} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex2-b} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex2-c} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex2-d} \\
        \hspace{-5mm} (a) $R_1$, $R_2$, $H$, and $V$ &
        \hspace{-4mm} (b) $R_1$, $H'$, and $V$ &
        \hspace{-4mm} (c) $R_2$, $H'$, and $V$ &
        \hspace{-4mm} (d) $R_2$ and $H^*$
    \end{tabular}
    \figcapup
    \caption{Finding H-V $k$-SJ result tuples of type 2 ($k = 4$)}
    \label{fig:hv:type2:ex}
    \figcapdown
\end{figure*}

@@

\noindent {\underline{\em Example 5.2.}} In Figure~\ref{fig:guard}a, segment $h_1$ has no left-covering rectangle in $R_2$ and thus has no trimmed segment. Segment $h_2$ has one left-covering rectangle in $R_2$, which is $\beta_1$. As the entire $h_2$ is covered by $\beta_1$, it is equivalent to its trimmed segment $h_2'$; see Figure~\ref{fig:hv:type2:ex}b. Segment $h_3$ has two left-covering rectangles in $R_2$, which are $\beta_2$ and $\beta_3$. The right endpoint of its trimmed segment $h_3'$, as shown in Figure~\ref{fig:guard}b, is decided by the right edge of $\beta_3$. Therefore, $H' = \set{h_2', h_3'}$. It is clear from Figure~\ref{fig:guard}b that $\J(R_1, H', V)$ has 3 tuples: $\bm{t}_1 = (\alpha, h_2', v_1), \bm{t}_2 = (\alpha, h_3', v_1)$, and $\bm{t}_3 = (\alpha, h_3', v_2)$.
\qed

@@

\extraspacing {\underline{\em Example 5.3.}} Consider tuples $\bm{t}_1$, $\bm{t}_2$, and $\bm{t}_3$ of $ \J(R_1, H', V)$ given in Example 5.2. For $\bm{t}_1 = (\alpha, h_2', v_1)$, its effective horizontal segment is $\texttt{DC}$ (see Figure~\ref{fig:hv:type2:ex}b. For $\bm{t}_2 = (\alpha, h_3', v_1)$, its effective horizontal segment is \texttt{EB}. For $\bm{t}_2 = (\alpha, h_3', v_2) \in \J(R_1, H', V)$, its effective horizontal segment is \texttt{EA}.
\vgap
